DeepSched: A Deep Representation Of Scheduling Policies For Heterogeneous Distributed Systems

### 2020-04-12 paper/core/exp_setup.tex
experimental setup review

The results are compared based on the execution time, as well as scheduling performance. For execution time, we measure the total time consumed by scheduling different number of tasks. For scheduling performance, we measure the total turnaround time for all scheduled tasks. Our network is supposed to achieve better execution time with similar performance to HEFT on previously seen data and slightly lower performance on unseen data.

@@

\subsubsection{Machine Encoder}
This module takes resource details as an input and learns a meaningful representation of them. It consists of one \emph{Conv1D} layer to extract the basic features of each processor, followed by one \emph{fully connected} layer to learn a compact representation of all processors, in order to be passed to the output modules. The common input features for each processor passed to this module are number of processor cores, core frequency and memory capacity. \\

@@

\subsection{Training}
The network is trained on HEFT scheduling outputs. Cross-entropy is used as a classification loss and mean squared error (MSE) is used as a regression loss. The summation of the two losses \ref{eq:l} is used to train the network using gradient descent with \emph{Adam} optimizer and a learning rate of $1e$-$5$. The network is trained for $100$ epochs. The task encoder only takes input of maximum number of tasks, so inputs of lower dimension are zero-padded along the length dimension to the maximum number ($84654$ tasks). \\

The training takes around $35$ minutes on \emph{Nvidia GTX} $1070$ and around $12$ hours on \emph{Nvidia GTX} $840m$, which is a relatively small time based on both \emph{GPUs} performance. \\

@@

\subsection{Inference}
Inference is performed on the trained network using both train and test data. We use the same $188$ resources information for all tests, however the input list of tasks is zero-padded to the maximum number of tasks, exactly like training.

@@

This is done by passing the schedule produced by the three methods through a simple simulation that runs the proposed schedule and calculates the average turnaround time of all tasks. Evaluation is also conducted on the execution time of each scheduling method, as the speed of the scheduling algorithm is one of our main targets.

>>>>

The results are compared based on the execution time, as well as scheduling performance. For execution time, we measure the total time consumed by scheduling different number of tasks. For scheduling performance, we measure the average turnaround time for all scheduled tasks. Our network is supposed to achieve better execution time with similar performance to HEFT on previously seen data and slightly lower performance on unseen data.

@@

\subsubsection{Machine Encoder}
This module takes resource details as an input and learns a meaningful representation of them. It consists of one \emph{Conv1D} \footnote{Convolution operation performed along one dimension only, usually used for regression.} layer to extract the basic features of each processor, followed by one \emph{fully connected} layer to learn a compact representation of all processors, in order to be passed to the output modules. The common input features for each processor passed to this module are number of processor cores, core frequency and memory capacity. \\

@@

\subsection{Training}
The network is trained on HEFT scheduling outputs. Cross-entropy is used as a classification loss and mean squared error (MSE) is used as a regression loss. The summation of the two losses \ref{eq:l} is used to train the network using gradient descent with \emph{Adam} optimizer and a learning rate of $1e$-$5$ with decay factor of $0.5$ every 20 epochs. The network is trained for $100$ epochs. The task encoder only takes input of maximum number of tasks, so inputs of lower dimension are zero-padded along the length dimension to the maximum number ($84654$ tasks). \\

The training takes around $35$ minutes on \emph{Nvidia GTX} $1070$ and around $10$ hours on \emph{Nvidia GTX} $840m$, which is a relatively small time based on both \emph{GPUs} performance. \\

@@

\subsection{Inference}
Inference is performed on the trained network using both train and test data. We use some of the train data, in order to test the ability of the network on previously seen data against HEFT. We use the same $188$ resources information for all tests, however the input list of tasks is zero-padded to the maximum number of tasks, exactly like training.

@@

This is done by passing the schedule produced by the three methods through a simple simulation that runs the proposed schedule and calculates the average turnaround time of all tasks. Evaluation is also conducted on the execution time of each scheduling method, as the speed of the scheduling algorithm is one of our main concerns.
